Punishment leads to greater sensorimotor learning but less movement variability compared to reward

### 2024-05-10 papers/2020-24/2024_roth_neurosci.qmd
fix typo

---
title: "Punishment leads to greater sensorimotor learning but less movement variability compared to reward"
type: "article"
author: "Roth AM., Lokesh R., Tang J., Buggeln JH., Smith C., Calalo JA., Sullivan SR., Ngo T., St. Germain L., Carter MJ., & Cashaback JGA."
year: "2024"
publication: "Neurosicence"
pdf: ""
doi: "https://doi.org/10.1016/j.neuroscience.2024.01.004"
github: ""
materials: ""
#supplementary: "https://www.sciencedirect.com/science/article/pii/S0306452224000125#s0150"
preprint: ""
toc: false
---

>>>>

---
title: "Punishment leads to greater sensorimotor learning but less movement variability compared to reward"
type: "article"
author: "Roth AM., Lokesh R., Tang J., Buggeln JH., Smith C., Calalo JA., Sullivan SR., Ngo T., St. Germain L., Carter MJ., & Cashaback JGA."
year: "2024"
publication: "Neuroscience"
pdf: ""
doi: "https://doi.org/10.1016/j.neuroscience.2024.01.004"
github: ""
materials: ""
#supplementary: "https://www.sciencedirect.com/science/article/pii/S0306452224000125#s0150"
preprint: ""
toc: false
---
